One page description

### 2016-12-08 publications/Journal/4-performance.tex
Updated captions of figures as well; PHOLD -> PHold consistently

Second, the \textit{Interconnect} model, a merge of PHOLD~\cite{PHOLD} and the \textit{HI} model of DEVStone~\cite{DEVStone}, creates $n$ atomic models, where each model has exactly one output port.
Similar to PHOLD, all models are connected to one another, but all through the same port: every atomic model receives each generated event (\textit{i.e.}, the event is broadcasted).
The model takes one parameter: the number of atomic models.
This benchmark shows the complexity of event creation, event routing, and simultaneous event handling.
An example for three atomic models is shown in Figure~\ref{fig:interconnect_model}.

Third, the \textit{PHOLD} model~\cite{PHOLD}, creates $n$ atomic models, where each atomic model has exactly $n-1$ output ports.
Each atomic model is directly connected to every other atomic model.
After a random delay, an atomic model sends out an event to a randomly selected output port.
Output port selection happens in two phases: first it is decided whether the event should be sent within the same kernel, or outside of the kernel.
Afterwards, a uniform selection is made between the possible atomic models.
The model takes two parameters: the percentage of remote events (determining the percentage of events routed to other kernels), and the percentage of high-priority events.
High-priority events are events generated in a very short time after the previous event.
This benchmark shows how the simulation kernel behaves in the presence of many local or remote events, in combination with a varying percentage of high-priority events.
An example for four atomic models, split over two kernels, is shown in Figure~\ref{fig:PHOLD_model}.

@@

\begin{figure}
    \center
	\includegraphics[width=\modelfraction\columnwidth]{fig/phold_model.pdf}
	\caption{PHOLD model for four models. Color denotes the two nodes.}
	\label{fig:PHOLD_model}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/queue_fixed_strong_speedup.eps}
	\caption{Queue model strong scaling speedup compared to \textit{dxex} \textit{NN} synchronization.}
	\label{fig:Queue_plot_strong}
\end{figure}

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/queue_fixed_weak_speedup.eps}
	\caption{Queue model weak scaling speedup compared to \textit{dxex} \textit{NN} synchronization.}
	\label{fig:Queue_plot_weak}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/interconnect_parallel.eps}
	\caption{Interconnect benchmark results for \textit{ON} and \textit{CN} synchronization.}
	\label{fig:interconnect_benchmark_parallel}
\end{figure}

\subsubsection{PHOLD}
In the PHOLD model, we first investigate the influence of the percentage of remote events on the speedup.
A remote event in this context is an event that is sent from an atomic model on one kernel to an atomic model on another kernel.
When remote events are rare, optimistic synchronization rarely has to roll back, thus increasing performance.
With more frequent remote events, however, optimistic synchronization quickly slows down due to frequent rollbacks.
Conservative synchronization, on the other hand, is mostly unconcerned with the number of remote events: the mere fact that a remote event can happen, causes it to block and wait.
Even though a single synchronization protocol is ideal throughout the whole simulation run, it shows that different synchronization protocols respond very differently to a changing model.

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/phold_remotes.eps}
    \caption{PHOLD benchmark results for multi core simulation using four kernels, with varying percentage of remote events.}
\end{figure}

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/phold_priority.eps}
	\caption{PHOLD benchmark results for multi core simulation using four kernels, with varying amount of high-priority events.}
	\label{fig:phold_priority}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/pdevs_no_sleep.eps}
	\caption{Queue speedup benchmark for PDEVS and synchronization with maximal concurrent events and trivial computational load}
	\label{fig:psim_plot_no_sleep}
\end{figure}

>>>>

Second, the \textit{Interconnect} model, a merge of PHold~\cite{PHold} and the \textit{HI} model of DEVStone~\cite{DEVStone}, creates $n$ atomic models, where each model has exactly one output port.
Similar to PHold, all models are connected to one another, but all through the same port: every atomic model receives each generated event (\textit{i.e.}, the event is broadcasted).
The model takes one parameter: the number of atomic models.
This benchmark shows the complexity of event creation, event routing, and simultaneous event handling.
An example for three atomic models is shown in Figure~\ref{fig:interconnect_model}.

Third, the \textit{PHold} model~\cite{PHold}, creates $n$ atomic models, where each atomic model has exactly $n-1$ output ports.
Each atomic model is directly connected to every other atomic model.
After a random delay, an atomic model sends out an event to a randomly selected output port.
Output port selection happens in two phases: first it is decided whether the event should be sent within the same kernel, or outside of the kernel.
Afterwards, a uniform selection is made between the possible atomic models.
The model takes two parameters: the percentage of remote events (determining the percentage of events routed to other kernels), and the percentage of high-priority events.
High-priority events are events generated in a very short time after the previous event.
This benchmark shows how the simulation kernel behaves in the presence of many local or remote events, in combination with a varying percentage of high-priority events.
An example for four atomic models, split over two kernels, is shown in Figure~\ref{fig:PHold_model}.

@@

\begin{figure}
    \center
	\includegraphics[width=\modelfraction\columnwidth]{fig/phold_model.pdf}
	\caption{PHold model for four models. Color denotes the two nodes.}
	\label{fig:PHold_model}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/queue_fixed_strong_speedup.eps}
	\caption{Queue model strong scaling speedup compared to \textit{dxex} \textit{NN} synchronization.
             Each kernel uses one thread, and has one physical CPU core allocated to it.}
	\label{fig:Queue_plot_strong}
\end{figure}

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/queue_fixed_weak_speedup.eps}
	\caption{Queue model weak scaling speedup compared to \textit{dxex} \textit{NN} synchronization.
             Each kernel uses one thread, and has one physical CPU core allocated to it.}
	\label{fig:Queue_plot_weak}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/interconnect_parallel.eps}
	\caption{Interconnect benchmark results for \textit{ON} and \textit{CN} synchronization, compared to \textit{dxex} \textit{NN} synchronization.
             Each kernel uses one thread, and has one physical CPU core allocated to it.}
	\label{fig:interconnect_benchmark_parallel}
\end{figure}

\subsubsection{PHold}
In the PHold model, we first investigate the influence of the percentage of remote events on the speedup.
A remote event in this context is an event that is sent from an atomic model on one kernel to an atomic model on another kernel.
When remote events are rare, optimistic synchronization rarely has to roll back, thus increasing performance.
With more frequent remote events, however, optimistic synchronization quickly slows down due to frequent rollbacks.
Conservative synchronization, on the other hand, is mostly unconcerned with the number of remote events: the mere fact that a remote event can happen, causes it to block and wait.
Even though a single synchronization protocol is ideal throughout the whole simulation run, it shows that different synchronization protocols respond very differently to a changing model.

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/phold_remotes.eps}
    \caption{PHold benchmark results using four kernels, with varying percentage of remote events.}
\end{figure}

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/phold_priority.eps}
	\caption{PHold benchmark results using four kernels, with varying amount of high-priority events.}
	\label{fig:phold_priority}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{fig/pdevs_no_sleep.eps}
	\caption{Queue speedup benchmark with $p = 1$, $q = 1$, and trivial computational load}
	\label{fig:psim_plot_no_sleep}
\end{figure}

### 2016-12-08 publications/Journal/5-hotswap.tex
Updated captions of figures as well; PHOLD -> PHold consistently

\subsubsection{Visualization of Communication}
To provide more insight in our benchmark models, we created a simple visualization of their simulation trace.
This trace visualizes the allocation of the model and all defined connections.
For each connection, the number of events transferred is annotated.
Examples are shown for the three benchmark models used before: Figure~\ref{fig:Queue_allocation}, Figure~\ref{fig:interconnect_allocation_parallel}, and Figure~\ref{fig:phold_allocation} show traces for the Queue, Interconnect, and PHOLD models, respectively.
Using this information, we notice that the Interconnect benchmark indeed has a lot of inter-kernel events.
Despite the similar structure, the PHOLD model does not have as many inter-kernel events.
These results are relevant information that can be used by the hotswapping component.

@@

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/interconnect_parallel_allocation.eps}
    \caption{Interconnect simulation trace for 6 models on 3 kernels.}
    \label{fig:interconnect_allocation_parallel}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/phold_parallel_allocation.eps}
    \caption{Phold simulation trace for multi core simulation using three kernels.}
    \label{fig:phold_allocation}
\end{figure}

>>>>

\subsubsection{Visualization of Communication}
To provide more insight in our benchmark models, we created a simple visualization of their simulation trace.
This trace visualizes the allocation of the model and all defined connections.
For each connection, the number of events transferred is annotated.
Examples are shown for the three benchmark models used before: Figure~\ref{fig:Queue_allocation}, Figure~\ref{fig:interconnect_allocation_parallel}, and Figure~\ref{fig:phold_allocation} show traces for the Queue, Interconnect, and PHold models, respectively.
Using this information, we notice that the Interconnect benchmark indeed has a lot of inter-kernel events.
Despite the similar structure, the PHold model does not have as many inter-kernel events.
These results are relevant information that can be used by the hotswapping component.

@@

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/interconnect_parallel_allocation.eps}
    \caption{Interconnect simulation trace for 6 atomic models on 3 kernels.}
    \label{fig:interconnect_allocation_parallel}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/phold_parallel_allocation.eps}
    \caption{PHold simulation trace for 6 atomic models on 3 kernels.}
    \label{fig:phold_allocation}
\end{figure}

### 2016-12-08 publications/Journal/6-allocation.tex
Updated captions of figures as well; PHOLD -> PHold consistently

\subsection{Performance Evaluation}
To evaluate the influence of model allocation, we define a new model, based on PHOLD~\cite{PHOLD}.
The model structure resembles a tree: an atomic model can have a set of children, with children being connected to each other recursively.

Unlike the Queue model, the width of the hierarchy is still present in the topology of the atomic models after direct connection.
The PHOLDTree model allows us to investigate speedup in terms of model allocation, by modifying the depth and width (fanout) model parameters.

The PHOLDTree model is similar in structure to models of gossiping in social networks~\cite{Gossip}.
The lookahead of an atomic node is the minimally allowed $\epsilon$, as is often the case in realistic models (\textit{e.g.}, if it is unknown what the lookahead might be).
We demonstrate the importance of allocation by comparing performance of a breadth-first versus a depth-first scheme.
Both options are automated ways of allocation that are independent of the model.

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtree.pdf}
    \caption{PHOLDTree model for depth 3 and width 2.}
    \label{fig:PHOLDTree_model}
\end{figure}

@@

\subsubsection{Inter-Kernel Synchronization (\textit{CN} and \textit{ON})}
Next, we run the model using two different allocation schemes: breadth-first and depth-first.
First, we explain both allocation schemes.

@@

\begin{figure}
   \center
   \includegraphics[width=\columnwidth]{fig/pholdtree_alloc_BF.pdf}
   \caption{PHOLDTree model breadth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_bfs}
\end{figure}

@@

\begin{figure}
   \center
   \includegraphics[width=\columnwidth]{fig/pholdtree_alloc_DF.pdf}
   \caption{PHOLDTree model depth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_dfs}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtreeallochighp.eps}
    \caption{PHOLDTree model performance using different allocation schemes.}
    \label{fig:PholdTree_plot_alloc_high}
\end{figure}

>>>>

\subsection{Performance Evaluation}
To evaluate the influence of model allocation, we define a new model, based on PHold~\cite{PHOLD}.
The model structure resembles a tree: an atomic model can have a set of children, with children being connected to each other recursively.

Unlike the Queue model, the width of the hierarchy is still present in the topology of the atomic models after direct connection.
The PHoldTree model allows us to investigate speedup in terms of model allocation, by modifying the depth and width (fanout) model parameters.

The PHoldTree model is similar in structure to models of gossiping in social networks~\cite{Gossip}.
The lookahead of an atomic node is the minimally allowed $\epsilon$, as is often the case in realistic models (\textit{e.g.}, if it is unknown what the lookahead might be).
We demonstrate the importance of allocation by comparing performance of a breadth-first versus a depth-first scheme.
Both options are automated ways of allocation that are independent of the model.

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtree.pdf}
    \caption{PHoldTree model for depth 3 and width 2.}
    \label{fig:PHOLDTree_model}
\end{figure}

@@

\subsubsection{Inter-Kernel Synchronization (\textit{CN} and \textit{ON})}
Next, we run the model using two different allocation schemes, based on Breadth-First Search (BFS) and Depth-First Search (DFS).
First, we explain both allocation schemes.

@@

\begin{figure}
   \center
   \includegraphics[width=\columnwidth]{fig/pholdtree_alloc_BF.pdf}
   \caption{PHoldTree model breadth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_bfs}
\end{figure}

@@

\begin{figure}
   \center
   \includegraphics[width=\columnwidth]{fig/pholdtree_alloc_DF.pdf}
   \caption{PHoldTree model depth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_dfs}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtreeallochighp.eps}
    \caption{PHoldTree model performance using different allocation schemes.}
    \label{fig:PholdTree_plot_alloc_high}
\end{figure}
